GPU-Accelerated Parallelization of Edge-Based Motion Detection Algorithms with the NVIDIA CUDA Framework

### 2015-12-11 documents/paper/paper.tex
Addressed error in algorithm
corrected the spelling of my name (because Kevin is not a bro)
added python section into intro

@@

	\nl Initialize $\boldsymbol{D}'$ to 0 $\forall i \in [0, m - 1], \forall j \in [0, n - 1]$\;
	\nl \ForEach {$i \in [0, m - 1]$} {
		\nl \ForEach {$j \in [0, n - 1]$} {
			\nl $x \gets 0$\tcp*{Number of differences in this region}
			\nl \ForEach{$i' \in [0, \frac{M}{n}]$} {
				\nl \ForEach{$j' \in [0, \frac{N}{n}]$} {
					\nl \If {$\boldsymbol{D}_{i + i', j + j'} \neq 0$} {
						\nl $x \gets x + 1$\;
					}
				}
			}
			\nl \If{$\frac{mn}{MN}x > \Gamma$} {
				\nl $\boldsymbol{D}'_{i, j} \gets 1$\;
			}
		}
	}
	\nl \Return $\boldsymbol{D}'$\;
	\
\end{algorithm}

@@

@@

\section*{Team}
\begin{itemize}
	\item \textbf{Emilio Del Vechhio}, Electrical and Computer Engineering `18
	\item \textbf{Kevin Lin}, Electrical and Computer Engineering `18
	\item \textbf{Senthil Natarjan}, Electrical and Computer Engineering `17
\end{itemize}

>>>>

\subsection{OpenCV and Python}
While CUDA is an excelent language for maximizing performance, it could be infeasible due to inexperience with C, time constraints, or lack of an NVIDIA GPU. To address these constraints, we also implemented our algorithms in Python using OpenCV. Python was chosen because it is very easy for inexperienced programmers to use and OpenCV was chosen because it offers many common image processing algorithms in a variety of languages.

@@

	\nl Initialize $\boldsymbol{D}'$ to 0 $\forall i \in [0, m - 1], \forall j \in [0, n - 1]$\;
	\nl \ForEach {$i \in [0, m - 1]$} {
		\nl \ForEach {$j \in [0, n - 1]$} {
			\nl $x \gets 0$\tcp*{Number of differences in this region}
			\nl \ForEach{$i' \in [0, \frac{M}{m}]$} {
				\nl \ForEach{$j' \in [0, \frac{N}{n}]$} {
					\nl \If {$\boldsymbol{D}_{\frac{Mi}{m} + i', \frac{Nj}{n} + j'} \neq 0$} {
						\nl $x \gets x + 1$\;
					}
				}
			}
			\nl \If{$\frac{mn}{MN}x > \Gamma$} {
				\nl $\boldsymbol{D}'_{i, j} \gets 1$\;
			}
		}
	}
	\nl \Return $\boldsymbol{D}'$\;
	\
\end{algorithm}

@@

\subsection{High Level Python Implementation}
Python is a widely used big-data programming language because of its extensive library support in such areas and its ease of use.

@@

\section*{Team}
\begin{itemize}
	\item \textbf{Emilio Del Vechhio}, Electrical and Computer Engineering `18
	\item \textbf{Kevin Lin}, Electrical and Computer Engineering `18
	\item \textbf{Senthil Natarajan}, Electrical and Computer Engineering `17
\end{itemize}
